\documentclass[11pt]{article}

    \usepackage[utf8]{inputenc}
    \usepackage{listings}
    \usepackage{kotex}
    \usepackage{color}
    \usepackage{float}
    \usepackage{hyperref}
    \usepackage{geometry}
    \geometry{a4paper}
    \geometry{margin = .5in}
    %\date{November 4th, 2018}
    
    \usepackage{graphicx}
    
    \title{Intro to Software Engineering: Assignment 11}
    \author{Harry Haisty}
    
    \begin{document}
    \maketitle
    \begin{enumerate}
    
    \item What is a naming model used for?
    \item[] To establish framework to control all the piece parts of the artifacts. 

    
    \item List the four major activities associated with software configuration management.
    \begin{enumerate}
        \item \textbf{Understanding the policy}, process activities, and the resulting artifcats that need to be managed.
        \item \textbf{Determining and defining the framework} that needs to be used to manage these artifacts.
        \item \textbf{Determining and bringing in any tools} that need to be brought in to facilitate the management of these artifacts. 
        \item \textbf{Training and ensuring that the agree-upon} configuration management process is practiced and adhered to.
    \end{enumerate}
    
    \item What are check-in and check-out?
    \item[]
    
    \item List three concerns you may need to look into before choosing a configuration management tool:
    \begin{itemize}
        \item How often is the automation tool updated and new releases made available?
        \item Is the specific automation tool supported? How is it supported?
        \item Does the vendor provide any formal education? In what form?
    \end{itemize}
    
    \item What are the build steps of a single program?
    \begin{itemize}
        \item Compile
        \item Link
    \end{itemize}
    
    \item What is linking and what are we linking in a build process?
    \item[] Linking is when you attach all of the eternally referenced items needed that are relatively limited in number. You attach limited, externally referenced items that are necessary to the code.
    
    \item Explain the difference between the \textit{view} and the \textit{modify} functions in the storage and access model of configuration management.
    \item[] 
    
    \item Name a tool from each of the three tiers of automating the configuration management activities.
    
    
    \end{enumerate}
    
    \end{document}