\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[margins=.5in]{geometry}
\usepackage{titling}


\setlength{\droptitle}{-5em}
\title{Linkedin Clinic Proposal}
\author{Harry Haisty | Association for Computing Machinery}
\date{February 2019}

\begin{document}

\maketitle

\section*{Synopsis}
The proposal is to host a Linkedin clinic for students of the College of Computer Science and Software Engineering, that is open to students of all majors. The information presented in the clinic will be primarily slanted towards STEM majors. 

\section*{Speaker(s)}
The speaker for this clinic will be Sarah Weldon, a professor in the department of Technical Communication. She has presented on how to create a professional Linkedin profile before, and will most likely reuse the resources she has included before. 

\section*{Refreshments}
This clinic will be hosted in the Atrium Building, in a small lecture hall. It is expected that anywhere between 20 and 50 students will participate. We will require: 
\begin{enumerate}
    \item Diet Soft Drinks [2 boxes]
    \item Regular Soft Drinks [2 boxes]
    \item Chocolate chip cookies [4 boxes]
    \item Bottled Water [1 pack]
    \item Variety pack of chips [2 packs]
    \item Cheese pizza [3 pizzas]
    \item Pepperoni pizza [3 pizzas]
\end{enumerate}

\section*{Additional Requests}
We are hoping to take professional pictures of the people attending the clinic, should they wish to have their picture taken. If there is a camera greater than 12MP, that would be excellent for taking pictures. 

\end{document}
