\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{color}
\usepackage{float}
\usepackage{geometry}
\geometry{a4paper}
\geometry{margin = .5in}

\usepackage{graphicx}

\title{Intro to Software Engineering: Assignment 3}
\author{Harry Haisty}


\begin{document}
\maketitle
\section*{Review Questions}
\begin{enumerate}
    \item \textbf{List two key reasons that have caused both software project successes and failures.}
    %Answer
    \begin{itemize}
        \item[-] \textit{Successes:} User Involvement
        \item[-] \textit{Failures:} Incomplete requirements and specifications
    \end{itemize}
    
    \item \textbf{From the definition of software engineering, list three areas that software engineering must touch on. }
    %Answer
    \begin{itemize}
        \item[-] analysis
        \item[-] specification
        \item[-] design
    \end{itemize}
    
    \item \textbf{List two of the three strategies cited by the 2004 U.S. General Accounting Office report as key to ensuring delivery of successful software.}
    %Answer
    \begin{itemize}
        \item [-] Methodical usage of metrics to gague cost, schedule, and performance targets. 
        \item [-] Focused attention on the software development environments.
    \end{itemize}
    
    \item \textbf{When and where was the term \textit{software engineering} first introduced?}
    %Answer
    \newline
    In a 1968 NATO conference held in Germany.
    
    \item \textbf{What are the eight principles for software engineering code of ethics recommended by the IEEE-CS/ACM Version 5.2 joint task force report?}
    %Answer
    \begin{enumerate}
        \item Software engineers shall act consistently with the public interest
        \item Software engineers shall act in a manner that is in the best interests of their client and employer, consistent with the public interest. 
        \item Software engineers shall ensure that their products and related modifications meet the highest professional standards possible. 
        \item Software engineers shall maintain integrity and independence in their professional judgment. 
        \item Software engineering managers and leader shall subscribe to and promote an ethical approach to the management of software development and maintenance. 
        \item Software engineers shall be fair to and supportive of their colleagues.
        \item Software engineers shall participate in lifelong learning regarding the practice of their profession and shall promote an ethical approach to the practice of the profession. 
    \end{enumerate}
    
    \item \textbf{What is meant by the term \textit{software engineering}?}
    %Answer
    \newline
    the discipline that focuses on the cost-effective development of of high-quality software systems. \textit{(Sommerville, 2010)}
    
    \item \textbf{Can a software engineer become a certified Professional Engineer (PE)? Explain.}
    %Answer
    \newline
    Not yet. In 1998, the Texas Board of Professional Engineers began to allow software engineers to earn engineering licenses, but it is a relatively new development and will likely take more time before software engineers can earn PE's. 
\end{enumerate}

\end{document}
