\documentclass[11pt]{article}

    \usepackage[utf8]{inputenc}
    \usepackage{listings}
    \usepackage{kotex}
    \usepackage{color}
    \usepackage{float}
    \usepackage{hyperref}
    \usepackage{geometry}
    \geometry{a4paper}
    \geometry{margin = .5in}
    
    \usepackage{graphicx}
    
    \title{Intro to Software Engineering: Assignment 8}
    \author{Harry Haisty}
    
    \begin{document}
    \maketitle
    \begin{enumerate}
        \item What are the two general characteristics of a good design that naturally evolve from requirements?
        \newline
        \textit{Completeness and consistency}
        
        \item What is the cyclomatic complexity of the design flow shown in Figure 8.4 where the diamond shapes represent decision branches and the rectangles are statements?
        \newline
        \textit{4}
        
        \item What are glue tokens and superglue tokens? Which contributes more to cohesion and why?
        \newline
        \textit{Glue tokens are the data tokens in a program that are located in more than one data slice. Superglue tokens are data tokens in a program that lie in every single slice of the program. Superglue tokens are more important to cohesion of a program because they are located throughout the entire program.}
        
        \item What are the levels of cohesion?
        \newline
        \textit{Coincidental, Logical, Temporal, Procedural, Communicational, Sequential, \& Functional}
        
        \item What are the levels of coupling?
        \newline
        \textit{Content, Common, Control, Stamp, \& Data}
        
        \item What are the six C-K metric for OO design?
        \begin{itemize}
            \item Weighted method per class
            \item Depth of inheritance tree
            \item Number of children
            \item Response for a class
            \item Coupling b/w objects
            \item Lack of cohesion in methods
        \end{itemize}
        
        \item What is a depth of inheritance tree (DIT) in C-K metrics, and why may a large DIT be bad for design?
        \newline
        \textit{The maximum length of inheritance from a given class to its root. A larger DIT means that there is more distance from the class to the root, giving more room for error.}
        
        \item In contrast to general design, what is of the most interest in UI design?
        \newline
        \textit{Consistency and ease of ability for the user to interact with the UI}
        \item List four of the eight rules of interface design presented by Schneiderman and Plaisant.
        \begin{enumerate}
            \item Strive for consistency
            \item Offer informative feedback
            \item Reduce short-term memory
            \item Permit easy reversal of action
        \end{enumerate}
    \end{enumerate}
    
    \end{document}